\iffalse
%\fi
\section*{Acknowledgments}
The list of people who have been part of path towards this result is, to me, more impressive than the result itself. I am not able to thank everyone here (the list is over 150 people, and that is still likely an underestimate)

I met Prof. Richard Milner in December, 2016. I am deeply thankful to have had him as an my research advisor and am lucky to have been part of his physics group. I'm also grateful to have had Prof. Janet Conrad and Prof. Will Detmold on my thesis committee and thank them for their helpful suggestions and guidance in completing my thesis.

School has been my central focus for as long as I can remember, and I had no shortage of amazing teachers to look up to. I want to specifically acknowledge my 5th grade teacher Mr. Magnuson, my middle school teachers Mr. Pineda, Mr. Phillips, and Mr. Noon (where I made a model of the Little Boy atomic bomb). 

My experience in high school was shaped heavily by many teachers, including:
\begin{itemize}
    \item Mr. Fuhr, in whose class I read Flatland, a book that sticks out to me to this day. Mr. Fuhr also once saw me sitting outside the high school around 9 PM doing homework waiting for my mom to pick me up, remarking I was 'really burning the midnight oil'. Quite the forshadowing for the next 10 years. 
    \item Mrs. Reed, who I hope to always do my homework for
    \item Mr. Landry, who I'm pretty sure was high most of the time but I will always remember for fostering an enjoyable class environment where I first started interacting with Haley more. 
    \item Mr. Thompson, in whose class I had a perfect 100 for quite some time, and remarked once to Mrs. Rice that I was `everyone's best student', which I tried hard for some time to keep true
    \item Ms. Makos, who made me feel like I didn't belong in her class
    \item Waldron and Shapland for treating students like people
    \item Mrs. Patierno and Se\~nora Morin, who never took attitude from any student    
\end{itemize} 

I want to specifically highlight my six AP course teachers, Mrs. Messina, Ms. Kis, Mr. McEvoy, Mrs. Rice, Mr. Logiudice, and Se\~nora Mastandrea. AP courses gave me a large advantage going into college, and I view it as critical in my college path proceeding as it did. I wish Mr. Logiudice pushed me harder when I was just playing Ninja Fishing in his class everyday, though. 

Ms. Horelick


Sports were also highly impactful, and I want to acknowledge Coach Maly and Cullen, Pancoast, and Dellasanta for their involvements. 


%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%% UMASS
%%%%%%%%%%%%%%%%%%%%%
I began at UMass Amherst as a chemical engineering major due to my success in AP Chemistry. Jessica Schiffman, who taught me that I would be overlooked, even if I had a 100 in a professor's course. Scott Auerbach, who taught me that Vanilla Ice's song was a pull from Queen's Under Pressure, 

and the friends I made at UMass - Christian Haughwot, who introduced me to the concept of research and into Prof. Miskimen's lab, Connor Walsh, 

Don Candela - if you want to do something, and i tell you its not a good idea, and you still want to do it, maybe you have a change

Jeffrey Davis
Wei Fan

Joe Smith

Fridericke Jentoft


Rory Miskimen

David Lawerence

Elton Smith

All JLab hockey guys

Susan Whitbourne

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% MIT 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

I made it through the part III exam with the tremendous support of Brandon, Chiara, Joe, and Loyd, along with the sage wisdom of Efrain, Rey, Axel, Field, and Yunjie. 

I'm grateful for the support of our MIT research group, consisting of Charles Epstein, Yimin Wang, Patrick Moran, Doug Hasell, Igor Korover, Ivica Friščić, Jan Berneaur, Ross Corliss, Steve Steadman,Xiaqing Lee

Bates, Ernie Ihloff, Chris Vidal, who taught me much about Lord of the Rings, Jim Kelsey, and I am happy to have known Chris Tschalaer.



Due to the extra space in my schedule from the AP class credit, I had room for another degree, which I felt should be either Physics or Math. I requested meetings with each departments' coordinator to discuss the possibility, and while the math department never replied to me, the physics  coordinator, Anthony Dinsmore, misinterpreted my request for a meeting about the major as a request for admission into the major, and enrolled me. 

Highlight Sangbaek Lee

Bolek, Christoph Paus 

Alex Diaz

The great staff in the physics department of MIT and LNS: Cathy Modica, Elsye Luc, Karen Dow, Anna Maria Convertino, Sydney Miller, Lauren Saragosa, Jack McGlashing


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% JLAB
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Calvin Mealer

I am thankful for the tremendous amount of support provided by individuals from JLab, in particular Susan and Melissa at the JLab ResFac, Calvin Mealer, Laura Hild from Jlab Scicomp who offered great technical insight, Kandice Carter at JLab publications, 

Members of the CLAS collaboration - Andrey Kim, Brandon Clary, David Riser, Dan Carman, Gagik Gavalian, Derek Glazier, Francois-Xavier Girod, Harut Avagyan, Latifa Elouadrhiri, Marco Contalbrigo, Maxime Defurne, Eugene Pasyuk, Volker Burket, Maurizio Ungaro, Marco Battaglieri, Paul Stoler, Stefan Diehl, Florian Hauenstein, Raffaella de Vita, Kyungseon Joo, Mac Mestayer, Nathan Baltzell, Veronique Ziegler, Valery Kubarovsky, Cole Smith, who explained much of the CLAS system with me and watched Univeristy of Virigia win the 2019 NCAA Championship while on shift together, Stepan Stepanyan

Mike Williams, Jesse Thaler


Xiangdong Ji, Kyle Shields, Brandon Kriesten, 

Gratitude is owed to Thomas Frank, who provided funding for first year MIT graduate students to more freely pursue interesting research, which allowed me to spend a great deal of time with Peter Fisher. 

My instructors at MIT will always stand out to me, and I thank them for their lectures and office hours: Senthil Todadri (Quantum Mechanics), Mehran Kardar (Stat. Mech - the most challenging physics course I ever took), Alan Guth (GR), Seth Loyd (Quantum Computation), Or Hen (Nuclear Physics), Lindley Winslow (Particle Physics), Yury Polansky (Fundamentals of Probability - the most challenging course I ever took, and for which I completely lacked a sufficient background), Leslie Kaelbling (Applied Machine Learning) Philippe Rigollet (Fundamentals of Statistics) and Bill Freeman (Advances in Computer Vision). 

Paul Acosta, Max Goncharov, Benedikt Maier, Zhangqier Wang


Jinine Abunandi

%%%%%%%%%%%%%%%%%%%%%
%%%% OTHER 
%%%%%%%%%%%%%%%%%%%%%
Those around me - Justin Buchanan, Madavin, Cathy, Coby Unger, Hayami Arakawa, Frank Taylor, Eileen Milner, Jon from binge bowl, Joe Griffin, for pulling me through stats, Stan Weisser, Rey Cruz-Torres, Peter FIsher

Matt Pietrek

Rick Kaufman

Jon / people from BUTPC

Larry Fiore

Inky Johnson
Javelin
ET the hip hop preacher

I want to also acknowledge Joe Recco, James Tilley, and Matt  Schiek, who I think of when I find myself disliking what I am working on. 

Tami Paluca, who looked out for me so much when no one else did

Nick Buzinsky

Tom Boettcher


My friends who have dealt with me canceling plans on them and in general putting school ahead of them for the past 10+ years; Nick Koulopoulos, Dan Lacross, Andrew Shepard, Brett Estrella, Nathan Alexander, Jake Reed, Skylar Whitney, Andrew Cantwell for liking every single one of my posts, Garnette


Wasalu Jaco
Nick Cambi

JLab/JSA Graduate Fellowship and APS DNP Travel Fund for providing support for

Sean Collier,


my Ph.D. study and dissemination and the FRANK FIRST YEAR FELLOWS


Grateful for Richard to allow me time to work on these problems

My sister Jen, who I remember telling me how the vascular system in plants worked when I was in kindergarten in our home in Winchester, who I look up to. Haley's cat Possum, who is 18 years old, adopted me. 

Lastly, Haley. 

\fi