\section{Exploring Structure through Scattering}\label{ch1:sec1:background}



Humanity interested in the structure of reality, atomic theory, subatomic, subnuclear, structure of this thesis.  The rest of this chapter discusses these advancments, and describes the theoretical background for this experiment. Chapter 2 descriptes the experiment, CHapter 5 the analysis, etc. Chapter 8 summarizes this work and discusses how this analysis will proceed in the near future and a path for future experiments. The appendix includes numerous technical details and upplemental plots.

As we increase the resolution (resolve features over smaller spatial distances), what we see is dependent on what resolution scale we are at. An exception to this case is if we are investigating point-like particles, which would have an identical response across all resolution scales

GPDs combine the kinematics of both elastic form factors and parton distributions. Andrey references 5, 6, and 7

\subsection{Discovery of the Proton}
Yimin has good references for this part
\subsection{Electron as a Nucleon Probe}

Include discussion of wavelength and momentum transfer (but in practice, limiting factor to resolution is lens system %https://advanced-microscopy.utah.edu/education/electron-micro/%

1961 hofstadter nobel prize (Andrey reference 1)
Andrey refrence 2 Friedman Kendall Tayleor scaling

Andrey thesis good write ups

Sangbaek:
proton has properties
Describe with QFT, words about QCD
role of experiment in studying proton structure
- proton discovery
- neutron discovery
- pointlike consitutents
- development of quark model
- scaling behavior and asymptotic freedom
- details about scattering experiments from first principles
- words about elastic scattering (mott scattering)
- Plot of elastic form factors, discussion of Ge and Gm, Rosenbluth formula
- Mention TPEX
- discussion of inelastic scattering
- Structure funcitons
- Discussion of spin and sum rules

Now discussion of DVEP:
GPDs, Wigner functions
relationships all the way around
some annoying math
Handbag diagram
Lepton hadron plane
Status of experiments and future (EIC mapping)




%Maybe someone will tell you to include something about the standard model



invariant mass is W 




Understanding the structure of matter has been a fundamental research pursuit for centuries. 


Proton not a point mass - it has structure



    \subsection{Structure of our World}
    - atomic theory
    - discovery of proton / nucleon
    - proton structure measurements
    - lepton scattering experiments, HERA, etc

